---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "", echo = FALSE)

show_files <- function(pkgs) {
  paths <- rev(fs::path_file(pkgs))
  cat(paths, sep = "\n")
}
```

This is a CRAN-like repository serving source and binary versions of selected R-packages from <https://forestgeo.github.io/>.

### Example

Setup the "repos" option to include this repository.

```
options(
  repos = c(getOption("repos"), forestgeo = "https://forestgeo.github.io/drat")
)
```

You can now install packages as usual. For example:

```R
install.packages("fgeo")
```

You can also update all packages with:

```R
update.packages()
```

Or update only the packages from this repository with:

```R
update.packages(repos = "https://forestgeo.github.io/drat")
```

### Latest source packages

(Earlier source packages are archived.)

```{r}
src_pkg <- fs::dir_ls(here::here("src/contrib"), glob = "*tar.gz")
show_files(src_pkg)
```

### All binary packages for windows

```{r}
bin_pkg <- fs::dir_ls(
  here::here("bin/windows/"), glob = "*zip", recursive = TRUE
)
show_files(bin_pkg)
```

### All binary packages for macosx

```{r}
bin_pkg <- fs::dir_ls(
  here::here("bin/macosx/"), glob = "*tgz", recursive = TRUE
)
show_files(bin_pkg)
```

---

"Drat" R Archive Template created by the [drat package](https://CRAN.R-project.org/package=drat)

