---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "#>", echo = FALSE)

show_files <- function(pkgs) {
  cat(fs::path_file(pkgs), sep = "\n")
}
```

This is a CRAN-like repository serving source and binary versions of released [__fgeo__ packages](https://forestgeo.github.io/fgeo/).

### Example

Setup the "repos" option to include the CRAN-like repository that serves __fgeo__ packages, i.e.  <https://forestgeo.github.io/drat>.

```
options(
  repos = c(getOption("repos"), forestgeo = "https://forestgeo.github.io/drat")
)
```

Install the latest stable version of all [fgeo packages](https://forestgeo.github.io/fgeo/) with:

```R
install.packages("fgeo")
```

Update packages, including the latest stable version of all [fgeo packages](https://forestgeo.github.io/fgeo/) with:

```R
update.packages()
```

### Available source packages:

```{r}
src_pkg <- fs::dir_ls(here::here("src/contrib"), glob = "*tar.gz")
show_files(src_pkg)
```

### Available binary packages for windows:

```{r}
bin_pkg <- fs::dir_ls(
  here::here("bin/windows/"), glob = "*zip", recursive = TRUE
)
show_files(bin_pkg)
```

### Available binary packages for macosx:

```{r}
bin_pkg <- fs::dir_ls(
  here::here("bin/macosx/"), glob = "*tgz", recursive = TRUE
)
show_files(bin_pkg)
```

---

"Drat" R Archive Template created by the [drat package](https://CRAN.R-project.org/package=drat)
