---
output: github_document
---

# CRAN-like repository for [__fgeo__ packages](https://forestgeo.github.io/fgeo/)

'Drat' R Archive Template created by the [drat package](https://CRAN.R-project.org/package=drat)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "#>", echo = FALSE)

show_files <- function(pkgs) {
  cat(fs::path_file(pkgs), sep = "\n")
}
```

## Example

Install the latest stable version of all [fgeo packages](https://forestgeo.github.io/fgeo/) with:

```R
these_repos <- c(getOption("repos"), "https://forestgeo.github.io/drat")
install.packages("fgeo", repos = these_repos)
```

Update to the latest stable version of all [fgeo packages](https://forestgeo.github.io/fgeo/) with:

```R
these_repos <- c(getOption("repos"), "https://forestgeo.github.io/drat")
update.packages(repos = these_repos)
```

## Available packages

Source and binary packages are available in the `gh-pages` branch of this repository.

### Source packages:

```{r}
src_pkg <- fs::dir_ls(here::here("src/contrib"), glob = "*tar.gz")
show_files(src_pkg)
```

### Binary packages for R 3.5 on Windows:

```{r}
bin_pkg <- fs::dir_ls(here::here("bin/windows/contrib/3.5"), glob = "*zip")
show_files(bin_pkg)
```

